---
title: "Practice Set 5"
author: 'Instructor: Saanchi Shah'
date: "2023-03-22"
output: html_document
---


## Overview

This practice set is modeled off content covered thru lab 5. 

Part 1.

Load the required packages to complete the assignment. For the first part use the travelnew.csv dataset.

```{r}

```

Create a scatterplot of accommodation cost against accommodation type. Before you do so, try to hypothesize the kind of trend you expect to see and why. A quick google search may help.
Hint: call in the dataframe first and use pipes to make it easier.
Please use the cheatsheet on the website and the documentation for data visualisation listed at the end of lab 4 [here](https://ggplot2.tidyverse.org).

```{r}

```

Part 2

Now read in the NC births dataset. 

```{r}

```

1. Rename at least 3 variables
2. Calculate the mean and standard deviation of birth weight. 
3. How many babies are premies and how many were low birth weight?
4. Do you think mothers who smoked are more or less likely to have babies with low birth weight? [Hint: create a two by two table] Use assigned readings or external resources to back up your answer when you report the difference.

```{r}


```

5. Likewise, what kind of an association did you expect between mothers' maturity and birth outcomes? Do the results align with your expectation?

```{r}


```

6. How many mothers are white vs not? Generate a plot for racial group vs mage. Use the cheatsheet to decide the type of plot that would make most sense(such as a boxplot) 


```{r}


```

7. Now create a plot for weight gained during pregnancy against race. Note: one is a categorical var and one is continuous. 

```{r}

```