---
title: "Practice1"
author: 'Instructor: Saanchi Shah'
date: "2023-03-20"
output: html_document
---

# This assignment is modeled off of the first lab. 

Part 1.

Load the tidyverse and dplyr packages.

```{r}
library(tidyverse)
library(dplyr)
```

Read the file in. Remeber to specify the sep = ";" argument. You may assign the dataframe to 'potions'.

```{r}
potions <- read.csv("/Users/saanchishah/Desktop/Spring_files/Harry Potter/Potions.csv", sep = ";")
```


Part 2.

1. Print the first 5 rows only.

```{r}
head(potions, n = 5)
```

2. How many observations and variables does this dataframe have?

72 observations and 5 columns

3. What are the types of variables in this dataset (use code)?

```{r}
str(potions) # provides attributes/labels as well

# observing each var like so is okay 
typeof(potions$Name)

```

4. How many beginner level potions exist in this dataset?
(Hint: select all columns)
```{r}
potions[potions$Difficulty.level == "Beginner", ] 
```
5. Create a table using the difficulty level and note missing levels.
```{r}
table(potions$Difficulty.level)
```

