---
title: "Practice2"
author: 'Instructor: Saanchi Shah'
date: "2023-03-20"
output: html_document
---

# Overview:

This practice set is modeled off the 2nd lab session. You can find the original dataset [here](https://www.kaggle.com/datasets/dgomonov/new-york-city-airbnb-open-data).

Part 1.

Load the required packages and read in the nyc airbnb file and assign it to 'nyc_airbnb'. You do not need to use the sep = ''. argument at all because the default sep will suffice. Simply use the filepath to read the csv file in.

```{r}
library(tidyverse)
library(dplyr)

nyc_airbnb <- read.csv("/Users/saanchishah/Desktop/Spring_files/nycairbnb2019.csv")
```


Part 2.

1. Select the following variables using 'pipes': id, name, price, minimum_nights, number_of_reviews, room_type, neighborhood_group, neighborhood. Assign this df to 'nyc_airbnb_subset'.

```{r}
nyc_airbnb_subset <- 
  nyc_airbnb %>% 
  select(id,
         name,
         price,
         minimum_nights,
         number_of_reviews,
         room_type,
         neighbourhood,
         neighbourhood_group)

```

2. Filter nyc_airbnb_subset by the neighborhood_group 'Manhattan' using pipes again. Call this df 'manhattan'.

```{r}
manhattan <- 
  nyc_airbnb_subset %>% 
  filter(neighbourhood_group == "Manhattan")
```

3.1 Provide the mean price of an airbnb in Mahattan using the summarize function.
3.2 How many airbnbs are in Manhattan?
3.3 What is the maximum value of number_of_reviews? 
3.4 What is the median number of minimum_nights spent at these airbnbs?

```{r}
# 3.1
manhattan %>% 
  summarize(mean_price = mean(manhattan$price),
            max_reviews = max(number_of_reviews),
            median_nights = median(minimum_nights))

```

