---
title: "Practice Set 4"
author: 'Instructor: Saanchi Shah'
date: "2023-03-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

This practice set is modeled off of Lab 4 (and things you may have learned so far). For this assignment, you will use the travel details dataset which can also be found [here](https://www.kaggle.com/datasets/rkiattisak/traveler-trip-data). As you may have noticed, kaggle is a cool resource to import data from to build on your coding skills.

Part 1. 

Load packages you may need for this assignment. Then read in the file, again remember R will use the default sep argument so you need not specify anything in your code. Assign this df to 'travel'.

```{r}



```


Part 2.

1. Rename any 3 variables of your choice and re-assign the df to 'travel'. Use pipes.

2. Group by nationality and calculate the mean trip duration and mean traveler age.

3. Create a new variable such that you can divide accommodation cost as 'costly' and 'cheap'. For example, you could choose a threshold of $1000 for the trip cost. Use the mutate function with if_else to do so. Read up the documentation on it if you can to do so. 

